QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-20 Response/Paper_Res.tex
Rev_V6.4

	\underline{Authors' Reply}: Given the importance of evaluating an agent's actions in DRL-based computation offloading approaches, we define the QoE maximization problem by considering several key performance factors. QoE is a time-varying performance measure that reflects user satisfaction and is influenced by more than just delay or energy consumption. On the other hand, investigating the trade-off between delay and energy consumption alone may not adequately address user demands or meet QoE requirements. To capture the agent’s personalized QoE needs, we designed an adaptive trade-off between task completion and cost reduction. In this model, the associated cost is a weighted sum of completion delay and energy consumption, with the weights dynamically adjusting based on the MD's preferences.\vspace{2mm}

>>>>

	\underline{Authors' Reply}: Given the importance of evaluating an agent's actions in DRL-based computation offloading approaches, we define the QoE maximization problem by considering several key performance factors. QoE is a time-varying performance measure that reflects user satisfaction and is influenced by more than just delay or energy consumption. On the other hand, investigating the trade-off between delay and energy consumption may not adequately address user demands and meet QoE requirements. To capture the agent’s personalized QoE needs, we designed an adaptive trade-off between task completion and cost reduction. In this model, the associated cost is a weighted sum of completion delay and energy consumption, with the weights dynamically adjusting based on the MD's preferences.\vspace{2mm}

### 2024-10-20 Revision/Paper_Rev.tex
Rev_V6.4

Additionally, we define $D_{i,j}^{\text{E}}(t)$ to represent the quantity of processing time slots allocated to task $z_{i,j}^{\text{E}}(t)$ when executed at EN $j$. This value is given by:
\begin{alignat}{1}
	D_{i,j}^{\text{E}}(t) = { \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over f_j^{\text{E}} \tau /  b_j(t)}.
	\label{14}  
\end{alignat}
We also define $E_{i,j}^{\text{E}}(t)$ as the energy consumption of processing at EN $j$ in time slot $t$ by MD $i$. This can be calculated as:
\begin{alignat}{1}
	E_{i,j}^{\text{E}}(t) = {D_{i,j}^{\text{E}}(t)  p_j^{\text{E}} \tau \over b_j(t)},  % = { \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over  f_j^{\text{E}}}p_j^{\text{E}} ,
	\label{15}  
\end{alignat}
where $p_j^{\text{E}}$ is a constant value which denotes the energy consumption of the EN $j$'s processor when operating at full capacity.

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i,j}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
\begin{alignat}{1}
	E_{i,j}^{\text{I}}(t) =  D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.
\begin{alignat}{1}
	E_i^{\text{O}}(t) = E_i^{\text{T}}(t) + \sum_{\mathcal{J}} \textcolor{blue}{y_{i,j}(t)} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t).
	\label{17}
\end{alignat}

@@

$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)$
\begin{alignat}{1}
	\;\;\;\,\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)} \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
where $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))= 0$ if task $z_i(t)$ is dropped. Correspondingly, we denote the energy consumption of task $z_i(t)$ when taking action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$ as $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, which is: \vspace{1.7mm}

$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+$
\begin{alignat}{1}
	\hspace{0.9cm} x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)}  E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}

>>>>

Additionally, we define $D_{i,j}^{\text{E}}(t)$ to represent the quantity of processing time slots allocated to task $z_{i,j}^{\text{E}}(t)$ when executed at EN $j$. This value is given by:
\begin{alignat}{1}
	D_{i,j}^{\text{E}}(t) =  {\,\, \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \,\,\, \over f_j^{\text{E}} \tau /  b_j(t)}.
	\label{14}  
\end{alignat}
We also define $E_{i,j}^{\text{E}}(t)$ as the energy consumption of processing at EN $j$ in time slot $t$ by MD $i$. This can be calculated as:
\begin{alignat}{1}
	E_{i,j}^{\text{E}}(t) =  { D_{i,j}^{\text{E}}(t)  p_j^{\text{E}} \tau \,\, \over b_j(t)},  % = { \lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over  f_j^{\text{E}}}p_j^{\text{E}} ,
	\label{15}  
\end{alignat}
where $p_j^{\text{E}}$ is a constant value which denotes the energy consumption of the EN $j$'s processor when operating at full capacity.

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
\begin{alignat}{1}
	E_{i}^{\text{I}}(t) =  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.
\textcolor{blue}{Therefore, let $E_i^{\text{O}}(t)$ denote the total energy consumption for the offloaded task $z_{i,j}^{\text{E}}(t)$ in time slot $t$, we have:}
\begin{alignat}{1}
	\textcolor{blue}{E_i^{\text{O}}(t) = E_i^{\text{T}}(t) +  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t) \,} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t)}.
	\label{17}
\end{alignat}

@@

$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)$
\begin{alignat}{1}
	\;\;\;\,\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)\, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
where $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))= 0$ if task $z_i(t)$ is dropped. Correspondingly, we denote the energy consumption of task $z_i(t)$ when taking action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$ as $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, which is: \vspace{1.7mm}
%\begin{alignat}{1}
%	\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+ x_i(t) E_i^{\text{O}}(t).
%	\label{22}  
%\end{alignat}

$\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+$
\begin{alignat}{1}
	\hspace{1.5cm} x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)
	  E_i^{\text{O}}(t')  \bigg).
	\label{22}  
\end{alignat}
